\documentclass[doublespace,prb,aps]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{svg}
\usepackage{xr}
\usepackage{amsthm,url,graphicx,booktabs,lipsum,color,bm,caption,subcaption,soul}
\usepackage{pifont,tikz,paralist,multirow,amssymb}
\usepackage{chemarr,natbib}
\usepackage{xifthen}
\usepackage{enumerate}
\usepackage{titlesec}
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
%\renewcommand{\thepoint}{C\,\thereviewer.\arabic{point}}

\renewcommand{\thepoint}{Comment\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses

\newenvironment{point1}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Associate Editor Comment~}} ---\ }
   {\par }

\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

% \newenvironment{point}

%    {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
%    {\par }

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~\thepoint} } ---\ }
   {\par }


\newcommand{\shortpoint}[1]{\refstepcounter{point}   \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---~#1  }

\newenvironment{reply}
   {\medskip \noindent \color{black} \begin{sf}\textbf{Reply}:\  }
   {\medskip \par \end{sf}}

\newenvironment{revision}
   {\medskip \noindent \color{blue} \begin{sf}\textbf{Revision}:\textit{\ }}
   {\medskip \par \end{sf}}


\newcommand{\shortreply}[2][]{\medskip \noindent \begin{sf}\textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip \end{sf}}

\makeatletter
\newcommand*{\addFileDependency}[1]{% argument=file name and extension
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{%
    \externaldocument{#1}%
    \addFileDependency{#1.tex}%
    \addFileDependency{#1.aux}%
}

\myexternaldocument{main}
%\externaldocument[I-]{main}


\def\thesubsubsection{\arabic{subsubsection}}
\titleformat{\subsubsection}[runin]
{\normalfont\bfseries}
{\indent\thesubsubsection)}{0.5em}{}


\begin{document}
\section*{Notes on revision made to manuscript Paper  \\
$\#$ct-2026-001787: Improving binding free energy predictions with Swap Monte Carlo for water sampling 
}
\vspace{10pt}

The authors sincerely thank the editor and all reviewers for their careful reading of the manuscript and for providing thoughtful, constructive comments. 
We have carefully considered each point and revised the manuscript accordingly. 
Significant changes in the revised manuscript are highlighted in \textcolor{blue}{blue} for the reviewers' convenience. 
Our point-by-point responses are provided below.
% Let's start point-by-point with Reviewer 1

%\section*{Response to the Associate Editor}
% General intro text goes here
%\begin{point1}
%For your work, I have received three independent review reports from experts 
%\end{point1}


%\begin{reply}
%Thank you so much for your constructive comments. 

%\end{reply}

\section*{Response to the reviewers}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
This is an interesting MC study on water sampling in the context of MD simulations/free energy calculations, 
and I believe it will be of significant interest to workers in the area. 
However, there are several aspects I would recommend improving.

% Point one description 
%\begin{reply}
%We thank the reviewer for the positive assessment and for the detailed suggestions, 
%which have helped strengthen the manuscript.
%\end{reply}

%%%%%%%%%%%%%%%%
\begin{point}
Some critical details are missing in methods; in general, the authors should provide enough detail someone should reproduce the work (e.g. give exact lambda spacing, form and parameters of soft core potentials, etc.). 
One specific thing I noticed is that it is unclear if the free energy calculations involve independent lambda values or are HREX simulations. 
This has major implications for understanding their results, so it is critical to explain.\label{comment_11}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for pointing this out. 
We have added more details in the revised manuscript, 
including the exact lambda spacing settings in SI information.
Beutler softcore potential with $\alpha=0.5$ is used for all alchemical transformations in this work. 
Hamiltonian Replica Exchange (HREX) is used for all RBFE and ABFE calculations, with exchange intervals of 1 ps and exchange attempts between all adjacent lambda windows.
Besides, REST2 enhanced sampling is applied to the FEP simulations, 
with the maxmium effective temperature of the solute region set to 600 K, 
and REST2 region is defined as the dummy atoms and the directly connected rotameric groups.
Details of the REST2 scale factors were also added in the schedule.json file in the SI information.
\end{reply}

\begin{revision}
Detailed $\lambda$ parameters for 16 $\lambda$-windows (RBFE) and 32 $\lambda$-windows (ABFE) are provided in the schedule.json in Supporting Information.
The other $\lambda$-windows for RBFE and ABFE calculations were generated by linear interpolation between the specified endpoints, ensuring smooth alchemical pathways.
Hamiltonian replica exchange was performed every 250 MD steps (1 ps) to enhance sampling across $\lambda$-windows,
REST2 strategy was applied to the alchemically perturbed ligand rotamers to further enhance sampling of ligand conformational space during transformations.
The REST2 region is defined as the dummy atoms and the directly connected rotameric groups, 
with the maxmium effective temperature of the solute region set to 600 K. \\
\dots \\
\newline
Beutler soft-core potential were employed for van der Waals interactions to 
mitigate singularities during decoupling, with standard soft-core parameters ($\alpha_{soft-core}$ = 0.5) to ensure stable sampling across $\lambda$-windows.
Electrostatic interactions were evaluated using Particle Mesh Ewald (PME) for accurate long-range treatment, with a real-space cutoff of 9~\textit{\AA}.
Dispersion correction was applied to account for long-range van der Waals interactions beyond the cutoff, ensuring accurate representation of bulk solvent effects on binding thermodynamics.
\end{revision}

\begin{point}
Clearly, water swap MC can achieve at least two things: (a) better equilibration of waters, and (b) better sampling of water states. 
Here, in most experiments, both are mixed together -- particularly, results are looking at improved water sampling IN free energy calculations. 
How much of the present gains could have been achieved simply by better equilibration? 
e.g. with simulations at independent lambda values, 
one could use water swap MC only during the equilibration phase to better equilibrate the water, 
then turn it off during the free energy calculations. 
How much would that have improved results and what would be the relative cost/benefit? 
(Even Schrodinger's work on GCMC relative free energy calculations, 
if read very carefully, highlights that most of the benefit from their GCMC algorithm actually comes from better equilbiration.)\label{comment_12}
\end{point}

% Ye: We should do this experiment and report the results.
% Our reply
\begin{reply}
We thank the reviewer for this insightful comment, which touches on an important mechanistic question. 
To disentangle the contributions of equilibration and production-phase sampling, 
we have performed additional control simulations in which SwapMC was applied exclusively during the equilibration phase and then disabled for the production phase. 
The results, presented in the revised manuscript Table 1, show that equilibration-only SwapMC recovers the most portion of the accuracy gains observed with full SwapMC, 
consistent with the reviewer's observation regarding Schrödinger's GCMC work. 
We have added a discussion of these findings and the corresponding cost/benefit analysis in the revised manuscript.
\end{reply}

\begin{revision}
Besides, to disentangle the contributions of equilibration and production-phase sampling,
we also performed RBFE calculations where SwapMC was only applied during the equilibration phase,
with standard MD used for production simulations (Equi. SwapMC Prod. NoSwapMC in Table~1).
The input structures for the equilibration-only SwapMC calculations kept the cavity waters, consistent with the "With CW." protocol, 
to ensure that any observed improvements could be attributed to enhanced sampling during equilibration rather than differences in initial water placement. \\
\dots \\
\newline
The comparision of results of equilibration-only SwapMC with full SwapMC indicate that the majority of the accuracy improvement arises from enhanced sampling during the equilibration phase,
which is consistent with the previous GCMC works that emphasized the importance of proper equilibration of cavity waters to accurate RBFE calculations~\cite{ross2020enhancing, ben2021fast}.
Nevertheless, the additional sampling during production phase with SwapMC provided further incremental improvements in accuracy, 
suggesting that continued water exchange throughout the simulation can further refine the free energy estimates by ensuring thorough sampling of the hydration landscape as the ligand undergoes alchemical transformation.
\end{revision}


\begin{point}
What about in systems where a binding site region partially collapses when water is absent? 
e.g. in Reference 34 a key finding is that in some cases, binding sites collapse and are hard to refill with water once a water is removed. 
Presumably, this approach would have a hard time dealing with such cases 
(as did the work in reference 34, but it might be even worse here); this should be addressed.\label{comment_13}
\end{point}

% Our reply
\begin{reply}
	TBD
\end{reply}

\begin{point}
It should be disclosed whether/where this code is available, if at all. 
It may be that this is only available in a commercial package (is Uni-FEP commercial?) and if so this should be stated. 
(And if that's the case, then the authors should give much more detail to allow reproduction of the work, 
see point 1 above, otherwise this would essentially just be a software advertisement.)\label{comment_14}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for raising this important point regarding transparency and reproducibility. 
We have added an explicit statement in the revised manuscript clarifying that the SwapMC method is implemented within Uni-FEP, which is a commercial software package.
In recognition of the reviewer's concern, we have substantially expanded the FEP calculation details in Results section to provide more simulation details — including the schedule parameter file in the SI, 
enhanced sampling strategies and long range interaction methods 
— sufficient for independent reimplementation of the method in other simulation engines.
\end{reply}

\begin{point}
Probably also cite OpenFF in connection with recent developments on force fields; in comparison with CGenFF and GAFF2, OpenFF has been more active in recent years. \label{comment_15}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for this suggestion. We have added the citation for OpenFF~\cite{Boothroyd2023, wang2024open, Hahn_2024} in the Introduction where recent force field developments are discussed, alongside CGenFF and GAFF2.
\end{reply}

\begin{revision}
Recent advances in force field development, including OPLS4~\cite{lu2021opls4}, CGenFF~\cite{vanommeslaeghe2012automationI, vanommeslaeghe2012automationII}, GAFF2~\cite{he2022recent}, and OpenFF~\cite{wang2024open,Boothroyd2023}, have substantially improved molecular representation accuracy~\cite{Hahn_2024}, 
yet inadequate sampling of conformational space—particularly concerning water molecule distributions in binding sites—remains a significant bottleneck limiting FEP reliability and domain of applicability~\cite{ross2020enhancing}.
\end{revision}

\begin{point}
It would be helpful to try and make the paper at least reasonably self-contained for those from outside the area, 
e.g. by adding single-sentence explanations when relevant. 
Concrete example: p11 line 11, "the Gumbel-Max Trick" is explained in terms of "Gumbel noise" which is unhelpful to me since I know neither the trick nor what Gumbel noise is. \label{comment_16}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for this comment. 
We have revised the relevant passage in the Methods section (Implementation of Swap Monte Carlo in OpenMM) to provide a self-contained explanation. The revised text now reads:
\end{reply}

\begin{revision}
This technique is a standard result from discrete probability theory: 
by adding independent Gumbel-distributed noise (a specific extreme-value distribution) to the log-probabilities of each candidate, 
and selecting the candidate with the maximum perturbed value,
one obtains an exact sample from the original categorical distribution.
Crucially, the argmax operation is parallelizable in $O(\log N_{\text{src}})$ time on GPUs, 
avoiding the serial bottleneck of computing cumulative distribution functions and performing sequential rejection sampling.
\end{revision}

\begin{point}
Concerning efficient evaluations of move proposals, 
could further optimizations be possible by pre-filtering candidate sites for obvious steric clashes (which would eliminate the need to do a full energy evaluation)? 
Or are the energy evaluations so efficient that this wouldn't provide further gains? 
(It would be good to briefly mention this in the paper.) \label{comment_17}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for this constructive suggestion.
Pre-filtering candidate sites for steric clashes is conceptually appealing; 
however, it introduces a non-trivial complication for the detailed balance condition. 
Specifically, if insertion candidates are first screened by a steric criterion before the Metropolis acceptance test is applied, 
the effective insertion probability $g^{ins}_{S_j}$ is no longer uniform over the destination region but is instead conditioned on passing the steric filter. 
This modifies the transition probability $G_{S_i \to S_j}$ in Eq. 7, 
and the reverse transition $G_{S_j \to S_i}$ would require a corresponding steric filter applied in the reverse direction 
— adding significant complexity to ensure microscopic reversibility is preserved. 
We therefore opted not to adopt this strategy in order to maintain the simplicity and theoretical transparency of the current acceptance criterion. \\
\newline
Furthermore, from a practical standpoint, the energy evaluation for all 18,000 candidate conformations is executed in a single parallel GPU kernel, 
such that the wall-clock cost is largely independent of the number of candidates evaluated. 
A steric pre-filter would therefore provide negligible computational benefit in our GPU-accelerated implementation. 
We have added a brief discussion of both points in the revised manuscript.
\end{reply}

\begin{revision}
Note that pre-filtering candidates by steric clashes prior to energy evaluation would complicate the detailed balance condition, 
as the effective insertion probability $g^{int}_{S_j}$ would no longer be uniform over the destination region; 
moreover, since all conformations are evaluated within a single GPU kernel that executes parallel energy evaluations for all candidates, 
such pre-filtering would provide no practical performance benefit.
\end{revision}

\begin{point}
page 18 line 24 and vicinity: Lack of improvement in some cases is blamed on force field accuracy, protein conformational sampling. Probably other example issues should also be listed and it should be made more clear that this is just a set of examples; for example, the benchmarking work of Hahn et al. has highlighted that in many cases, ligand pose quality and system prep (selection of protonation states etc.) are a dominant source of error, and these factors aren't even mentioned here. \label{comment_18}
\end{point}

% Our reply
\begin{reply}
We thank the reviewer for this important observation. 
The reviewer is correct that the list of potential error sources in our original discussion was incomplete.
We have also revised the language to make clear that these represent illustrative examples of the various factors 
that may contribute to prediction error, rather than an exhaustive taxonomy.
\end{reply}

\begin{revision}
These observations validate the mechanistic premise that SwapMC specifically addresses water-sampling-limited ABFE scenarios, 
improving accuracy when water reorganization is the bottleneck but providing minimal benefit when other factors dominate the prediction error. 
Such factors include, but are not limited to, force field inaccuracies, 
insufficient protein conformational sampling, 
ligand pose quality and binding mode ambiguity, 
and errors in system preparation such as protonation state assignment 
and tautomeric state selection 
— factors that have been identified as dominant sources of error in practical FEP benchmarking contexts~\cite{Hahn_2024}.
\end{revision}


\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
The authors reported an MC method for sampling water molecules in buried pockets 
that appears to help the convergence of free energy calculations for such systems. 
The topic is of interest to the readership of JCTC and results are interesting. 
The authors need to address the following few comments before the paper can be published:

%%%%%%%%%%%%%%%%
\begin{point}
While the formulas appear correct for the MC water swap, 
the parallel evaluations of multiple MC moves might break the detailed balance condition. 
In particular, after all the potential insertion conformations are sequentially evaluated, 
"the first conformation to satisfy the Metropolis criterion (random number $\le$ ASi→Sj ) is accepted, and the iteration proceeds to Step 5." 
Is there a particular fixed sequence about the different positions and orientations of the candidate water configuration for insertion? 
Or is it random as well? 
What does 'first' here mean? "first" in calculation order that satisfies the MC acceptance or 'first' in the predetermined order? 
Depending on the implementation details, the detailed balance condition may break. \label{comment_21}
\end{point}

\begin{reply}
We thank the reviewer for this careful and perceptive comment. The reviewer correctly identifies a subtlety that requires clarification.

In our implementation, the 18,000 candidate insertion conformations per swap attempt 
are generated by combining 300 uniformly sampled insertion sites with 60 approximately uniformly distributed orientations (sampled via quaternion parameterization of SO(3)). 
These conformations are re-generated independently for each swap attempt, 
so the sequence is effectively random across attempts. 
Within a single attempt, conformations are evaluated in a fixed order, 
and "first" in Step 4 refers to the first conformation in this order that satisfies the Metropolis acceptance criterion.
Since the conformation set is independently resampled at each attempt, 
the insertion probability $g^{ins}_{S_j}$ remains uniform over the destination region, 
and detailed balance is preserved as derived in Eq. 7.
We have substantially expanded the relevant section in the Methods to make this point explicit and to clarify the implementation details, 
including the fixed ordering and the independence of each acceptance test.
\end{reply}

\begin{revision}
The 18,000 conformations are re-generated independently for each swap attempt, ensuring the insertion probability $g^{(ins)}_{S_j}$ remains uniform over the destination region as required by Eq.~7.\\
\dots \\
Conformations are evaluated in a fixed order within each attempt, and the first conformation to satisfy the Metropolis criterion (random number  $< A_{S_i \to S_j}$) is accepted.
\end{revision}


%%%%%%%%%%%%%%%%
\begin{point}
The validation on free energy calculation is good, but not quite sufficient. 
I recommend control simulations on more basic systems to validate the theory and implementation. 
For example, the authors can perform simulations on ideal gas systems where analytical solutions are available, 
and a box of water molecules where water exchange is not a problem to compare the simulation results with NPT without MC swap.\label{comment_22}
\end{point}

\begin{reply}
We thank the reviewer for this suggestion. 
The SwapMC method is currently implemented as an integral component of the alchemical FEP workflow in Uni-FEP, 
and constructing standalone validation systems such as ideal gas or pure bulk water boxes 
would require substantial re-engineering that is beyond the scope of the present work. \\
\newline
We would like to humbly note that the theoretical correctness of the acceptance criterion is established analytically through the detailed balance derivation in Eqs. 2–8. 
Empirically, the robustness of results across 94 RBFE and 67 ABFE calculations 
— with SwapMC consistently driving cavity hydration toward physically reasonable values (Fig. 2), 
improving accuracy across diverse targets (Tables 1–2), 
and yielding results insensitive to initial water configuration 
— provides strong evidence for a correct implementation. 
We hope the reviewer finds these validations adequate. 
We also note that refactoring SwapMC into a standalone, 
framework-independent module is planned for future work, 
which will facilitate validation against simple reference systems and broader community adoption.
\end{reply}

%%%%%%%%%%%%%%%%
\begin{point}
The analysis of AbFEP results needs improvement. 
Experimental dG has contributions from interaction free energy with the ligand and the apo to holo protein conformational change, 
with the later missing in short AbFEP simulations. 
Instead of comparing the raw predicted dG with exp, the authors are encouraged to separate out the systematic shift as compared to exp (related to apo to holo conformational free energy missing for all ligands), 
and then access the effort of MC swap on both the systematic error and the ranking order error. \label{comment_23}
\end{point}

\begin{reply}
We thank the reviewer for this valuable suggestion. 
The reviewer correctly points out that the systematic offset between predicted and experimental absolute binding free energies 
— arising from incomplete sampling of the apo-to-holo conformational change — affects all ligands within a given target approximately equally. 
We have revised the ABFE analysis accordingly: for each protein target, we subtract the mean signed error across all ligands to remove this systematic contribution and report the resulting shifted RMSE. 
We additionally report Kendall's ranking value $\tau$ to evaluate ranking accuracy independently of absolute errors. 
Table 2 and the surrounding discussion have been updated to reflect this analysis.
\end{reply}

\begin{revision}
In addition to the raw $\Delta G$ RMSE and $R^2$, we report the shifted dG RMSE 
— computed after subtracting the per-target mean signed error to remove the systematic offset attributable to incomplete apo-to-holo conformational sampling 
— and Kendall's $\tau$ to assess rank-ordering accuracy independently of absolute errors. \\
\dots 
\newline
Concurrent $R^2$ improvements for these systems (CDK2: 0.09 $\to$ 0.55, TYK2: 0.40 $\to$ 0.47) and Kendall's $\tau$ (CDK2: 0.20 $\to$ 0.38, TYK2: 0.38 $\to$ 0.50)
indicate that SwapMC not only reduced absolute errors but also improved rank-ordering correlation with experimental data, suggesting more reliable discrimination of binding affinity differences. 
Similar improvements appeared for BACE (RMSE 3.27 $\to$ 2.68 kcal/mol) and MCL1 (2.05 $\to$ 1.67 kcal/mol), supporting broad utility across targets with water-sensitive binding sites. \\
\dots
\newline
Thrombin showed a small increase in raw $\Delta G$ RMSE (1.67 $\to$ 1.82 kcal/mol), 
yet the shifted dG RMSE dropped substantially (1.31 $\to$ 0.57 kcal/mol) 
and Kendall's $\tau$ improved markedly (0.38 $\to$ 0.60), 
indicating that SwapMC corrected a systematic bias present in the no-SwapMC predictions 
at the cost of a modest increase in raw RMSE for some individual ligands.
\end{revision}

%%%%%%%%%%%%%%%%
\begin{point}
The raw data for both RbFEP and AbFEP need to be included in the SI.\label{comment_24}
\end{point}

\begin{reply}
We thank the reviewer for this request. 
We have included the complete raw data for all RBFE and ABFE calculations as Supporting Information. 
Specifically, the SI now contains: (1) per-edge $\Delta \Delta G$ predictions and experimental values for all 94 RBFE transformations across the eight water-displacement benchmark systems; 
and (2) per-ligand $\Delta G$ predictions and experimental values for all 67 ABFE calculations across the eight JACS benchmark targets. 
Both with-SwapMC and without-SwapMC results are provided for all entries.
\end{reply}

\bibliography{ref,common_ref}
\bibliographystyle{chicago}
\end{document}
